Extracting all spectra for NEON mapped stems

### 2020-09-02 R/spectral-lib.Rmd
setting a directory for the spectral lib gist
to avoid having tons of files living in the R folder, keep them in the raw_data folder for now

```{r get-veg-data}
dir.create('data')
zipsByProduct(dpID = "DP1.10098.001",
              savepath = "data",
              check.size = FALSE)
stackByTable("data/filesToStack10098", folder = TRUE)
```

>>>>

```{r get-veg-data}
# set output directory within the analysis/data/raw_data path 
out_dir <- here::here("analysis","data","raw_data","spectral-lib")
dir.create(out_dir)
dir.create(file.path(out_dir, 'data'))

zipsByProduct(dpID = "DP1.10098.001",
              savepath = file.path(out_dir, 'data'),
              check.size = FALSE)
stackByTable(file.path(out_dir, "data","filesToStack10098"), folder = TRUE)
```
